---
title: "JP Addresses"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

data_dir <- here::here("data")
ken_all <- file.path(data_dir, "KEN_ALL.CSV")
```

Most of the code here is from https://uribo.hatenablog.com/entry/2019/12/22/102452. Thanks [\@uribo](https://github.com/uribo)!

### Get data

```{r get_data, eval=!file.exists(ken_all)}
dir.create(data_dir, showWarnings = FALSE)
temp <- tempfile(fileext = ".zip")
download.file("https://www.post.japanpost.jp/zipcode/dl/oogaki/zip/ken_all.zip", temp)
unzip(temp, exdir = data_dir)
```

### Load data

```{r load_data}
library(dplyr, warn.conflicts = FALSE)
library(zipangu)
library(stringr)

df <- read_zipcode(path = ken_all, type = "kogaki") %>%
  select(jis_code, zip_code, prefecture, city, street, is_cyoumoku) %>% 
  # add rowid at this stage because grouped-df might be rearranged depending on the version of dplyr...
  tibble::rowid_to_column()

nrow(df)

head(df)
```

### Duplicated columns

All duplicated columns are only these two pairs:

```{r show_dup}
df %>% 
  group_by(zip_code, city, street) %>% 
  filter(n() > 1)
```

Let's choose the first ones.

```{r remove_dup}
df <- df %>% 
  group_by(zip_code, city, street) %>% 
  filter(row_number() == 1) %>%
  ungroup()
```

### Multi-line columns

Multi-line columns can be detected by detecting the imbalance of parenthesis.
Before running into it, check these assumptions are true:

1. Opening parenthesis is always paired with a closing parenthesis
2. Only half-width parenthesis is used

```{r num_of_parenthesis}
sum(str_count(df$street, fixed("(")))
sum(str_count(df$street, fixed(")")))
# 全角
sum(str_count(df$street, fixed("（")))
sum(str_count(df$street, fixed("）")))
```

Seems fine. Let's move on.

```{r mark_multi_line}
df_marked <- df %>%
  mutate(
    opening_paren = cumsum(str_count(street, fixed("("))),
    closing_paren = cumsum(str_count(street, fixed(")"))),
    # increase id when
    # 1) the last line is a single-line row
    # 2) the last line is the end of multi-line rows
    row_group_id  = cumsum(lag(opening_paren == closing_paren, default = 0))
  )

# multi-line rows
df_marked %>%
  group_by(row_group_id) %>% 
  filter(n() > 1) %>% 
  head()
```

Confirm `jis_code`, `zip_code`, `prefecture`, `city` and `is_cyoumoku` are the same value within the same `row_group_id`. If any of them differ, it means `row_group_id` was numbered wrongly.

```{r validate_multi_line}
nrow(distinct(df_marked, row_group_id))
nrow(distinct(df_marked, jis_code, zip_code, prefecture, city, is_cyoumoku, row_group_id))
```



```{r concat_multi_line}
df <- df_marked %>%
  group_by(jis_code, zip_code, prefecture, city, is_cyoumoku, row_group_id) %>%
  # ensure the rows are in the original order
  arrange(rowid) %>%
  summarise(street = paste(street, collapse = ""), n = n()) %>% 
  ungroup()

# check if the streets are concatinated fine
df %>%
  filter(n > 1) %>%
  select(zip_code, street) %>% 
  head()
```

```{r clean_multi_line}
# remove unncessary columns
df <- df %>% 
  select(jis_code, zip_code, prefecture, city, is_cyoumoku, street)
```

### Extract streets

The contents of parenthesis in `streets` needs to be extracted.

But, it seems some columns have multiple parenthesis, which might be problematic.

```{r max_paren}
max(str_count(df$street, "\\(.*\\("))
```

So, which columns have multiple parenthesis?

```{r multi_paren}
str_subset(df$street, "\\(.*\\(")
```

These rows don't need to be extracted, so let's ignore them and consider only one parenthesis.
We split `streets` into two part `base` (the part before parenthesis) and `variants` (the part within parenthesis).
For example:

```
大通り(1〜3番地)
--+-- --+----
  |     |
  |     +-- variants
  +--------- base
```

But, be careful, if the contents of parenthesis doesn't contain `、`, `〜`, or `・`, we can leave them as it is.
For example,

```
名駅ミッドランドスクエア(高層棟)(47階)
--+----------------------------
  |
  +-- base
```

OK, let's move on.

```{r extract}
library(tidyr)

df_extracted <- df %>%
  extract(street, c("base", "variants"), "^([^\\(]+)(\\([^\\(]*[、〜・][^\\(]*\\))?$")

df_extracted %>% 
  filter(!is.na(variants)) %>% 
  head
```

```{r prepare_for_split}
df_extracted <- df_extracted %>% 
  filter(!is.na(variants)) %>% 
  # extract 丁目|番地
  extract(variants, c("variants", "unit"), "^(.*?)(丁目|番地)?$")
```

```{r split}
df_extracted <- df_extracted %>% 
  # replace 、 inside 「」 to prevent them from being split
  mutate(variants = str_replace_all(variants, "「.*?」", swap_comma)) %>% 
  # split by 、
  separate_rows(variants, sep = "、") %>% 
  # restore 、 inside 「」
  mutate(variants = restore_comma(variants))

# check the contents
str_subset(df_extracted$variants, "「|」")
```